README

### 2022-10-25 rmd/README.Rmd
readme

Title: Intentional release of native species undermines ecological stability
Authors: Akira Terui, Hirokazu Urabe, Masayuki Senzaki, Bungo Nishizawa

@@

```{r}
sessionInfo()
```

>>>>

**Title:** Intentional release of native species undermines ecological stability

**Authors:** Akira Terui, Hirokazu Urabe, Masayuki Senzaki, Bungo Nishizawa

@@

```{r}
source(here::here("code/library.R"))
sessionInfo()
```
